Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-06 paper/manuscript.tex
Some tweaks to manuscript

\begin{suppfigure}
\centerline{\includegraphics[width=0.6\textwidth]{figs/S02_SangerSeq/SangerSeq.pdf}}
\caption{\label{suppfig:SangerSeq}
{\bf Sanger sequencing of 30 clones from the mutant plasmid libraries.} 
(A) 
(B)
(C)
(D)
(E)
}
\end{suppfigure}

>>>>

\begin{suppfigure}
\centerline{\includegraphics[width=0.6\textwidth]{figs/S02_SangerSeq/SangerSeq.pdf}}
\caption{\label{suppfig:SangerSeq}
{\bf Sanger sequencing of 31 clones from the mutant plasmid libraries.} 
(A) There were an average of $\sim$1.4 codon mutations per clone across the three plasmid mutant libraries.
(B) A mixture of one-, two-, and three-nucleotide mutations were present, with slightly fewer triple-nucleotide changes than expected.
(C) Nucleotide frequencies were uniform in the codon mutations.
(D) The mutations were distributed relatively evenly across the length of the HA coding sequence.
(E) We calculated the pairwise distances between mutations for clones carrying more than one mutation.
The cumulative distribution of the distances is shown in the red line.  
}
\end{suppfigure}
